---
title: "practical 1"
author: "Narges Yarahmadi Gharaei"
date: "2023-05-16"
output:
  pdf_document: default
  html_document: default
---

installing packages and importing them



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE}
library(tidyverse) 
library(datasauRus)
library(knitr)

```

dataset

```{r}
datasaurus_dozen

```

check dataset's dimension

```{r}
print( nrow(datasaurus_dozen))
print( ncol(datasaurus_dozen))
print( dim(datasaurus_dozen))

```

count each dataset : every dataset inside datasaurs_dozen has 142 points

```{r}
datasaurus_dozen %>% count(dataset)
```

filtering data (here dino) and put in dino_data

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
```

```{r}
dino_data 
```

plot dino data

```{r}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

check the corelation of dino dataset

```{r}
dino_data_r = dino_data %>% summarize(dino_data_r = cor(x, y))
print(dino_data_r)
```

question 3 : do the same steps for star dataset

```{r}
star_dataset <- datasaurus_dozen %>%  filter(dataset == "star")
ggplot(data = star_dataset, mapping = aes(x = x, y = y)) + geom_point()
star_dataset_r = star_dataset %>% summarize(star_dataset_r = cor(x, y))
print(star_dataset_r)

```

question 4 : do the same steps for star dataset

```{r}
circle_dataset <- datasaurus_dozen %>%  filter(dataset == "circle")
ggplot(data = circle_dataset, mapping = aes(x = x, y = y)) + geom_point()
circle_dataset_r  = circle_dataset %>% summarize(circle_dataset_r = cor(x, y))
print(circle_dataset_r)

```




As the correlation coefficient (r) exhibits a nearly identical and considerably low negative value, along with the datasets having almost identical mean values, it becomes challenging to ascertain the most suitable linear fit for Y as a function of X.


question 5:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```




```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y))
```

